---
title: "Team C2"
author: "Lee"
date: "10/12/2019"
output: pdf_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, png, grid)
```

 
## Data Cleaning and EDA part
```{r}
NumericDataRaw <- read_csv("Numeric.csv")
TextDataRaw <- read_csv("ChoiceText.csv")
``` 
Import Client specified IDs
```{r}
ExcludedIDs = readxl::read_xlsx(path = "Need to be excluded IDs.xlsx",
  sheet = 3,col_names = TRUE,col_types = "text")%>%select(1)%>%pull()
print(paste0("Number of IDs Client would like to exclude: ",
  as.character(length(ExcludedIDs))))
```
## --- Import ends here

Tag Original Dataset with ID valid status, Valid ID will be tagged "Valid" in the column:"ValidReponse", Invalid ones will be tagged "Invalid"
```{r}
TextDataRaw = TextDataRaw%>%
  mutate(ValidResponse = if_else(ResponseId %in% ExcludedIDs,
  "Invalid","Valid"), ValidResponse = as.factor(ValidResponse),Q103 = as.factor(Q103))
NumericDataRaw = NumericDataRaw%>%
  mutate(ValidResponse = if_else(ResponseId %in% 
  ExcludedIDs,"Invalid","Valid"),
  ValidResponse = as.factor(ValidResponse),Q103 = as.factor(Q103))
```
Split them just in case
```{r}
TextRawWithoutExIDs = filter(TextDataRaw,!ResponseId %in% ExcludedIDs)
TextRawofExIDs = filter(TextDataRaw,ResponseId %in% ExcludedIDs)
```
## --- Tag and split ends here


```{r}
geo=select(TextDataRaw,Q103_1_x:Q103,ValidResponse)%>%
  slice(-(1:2))%>%
  mutate(Q103 = as.factor(Q103),Q103_1_x = as.numeric(Q103_1_x),Q103_1_y = as.numeric(Q103_1_y))

ggplot(geo)+aes(x = Q103_1_x,y = Q103_1_y,color = Q103)+
  geom_point()+facet_wrap(geo$ValidResponse)
```
What's the map actually used in the survey?? 

This should be the map from final survey version. 
```{r}
img <- readPNG("Picture1.png")
 grid.raster(img)
```

## Check counts in each region
```{r}
ggplot(geo) + aes(x = Q103) + geom_bar()+geom_text(stat='count', 
aes(label=..count..), vjust=0)+facet_wrap(geo$ValidResponse)
```
We have 76 NA values in geo questions. the population in this category is larger than Midwest and Southwest. Can we simply excluding them?

## --- Initial visual ends here

## --- Seperate Demographics
Seperate the Demographic part, setting them as adequate type
```{r}
DemoText = select(TextDataRaw,Q10:Q28,ValidResponse,ResponseId)%>%slice(-(1:2))%>%
  mutate_at(.vars = c(1:4,8:9,12:13,16:21), .funs = as.factor)%>%
  mutate_at(.vars = 5:6, .funs = as.numeric)%>%mutate(Q13 = as.list(strsplit(Q13, ",")),
  Q18 = (as.list(strsplit(Q18, ","))))
```
Combine "Day care" with"Daycare"
```{r}
DemoText = DemoText%>%mutate(Q13_6_TEXT = if_else(DemoText$Q13_6_TEXT == "Daycare","Day care",
          DemoText$Q13_6_TEXT))
```
Right now, two lists are in the result, need to separate them into columns

## --- Separation For Q13
```{r}
Q13Text = select(DemoText,Q13,ValidResponse,ResponseId)%>%
  unnest(Q13)%>%spread(key = Q13,value = Q13)%>%
  mutate_at(3:9, ~replace(., !is.na(.), 1.))%>%
  mutate_at(3:9, ~replace(., is.na(.), 0.))
```
## --- Sep for Q13 ends here


## --- Similarily Separation for Q18
```{r}
Q18Text = select(DemoText,Q18,ValidResponse,ResponseId)%>%
  unnest(Q18)%>%spread(key = Q18,value = Q18)%>%select(-3)%>%
  mutate_at(3:25, ~replace(., !is.na(.), 1.))%>%
  mutate_at(3:25, ~replace(., is.na(.), 0.))
# Bird's colname is buggy replace it
colnames(Q18Text)[colnames(Q18Text)=="Bird (i.e."] <- "Bird"
```
## --- Sep for Q18 ends here

## At this point, we will have DemoText as the demographic part cleaned. Q13Text and Q18Text as the suppliment table to those two questions.
## Be aware that a lot of the input had translated into factors, which depends on the graph you would like to plot, may results in some issues.
## Have fun!!



